---
title: "dogtrack: GPS preprocessing workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dogtrack: GPS preprocessing workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)
library(dogtrack)
```

## Overview

`dogtrack` implements a four-stage GPS quality-control pipeline for
free-roaming domestic dog movement data. It is designed to process
data from multiple field sites simultaneously, with site-specific
thresholds automatically derived from static GPS test files.

## Minimal usage

```{r}
dog_data_flagged <- run_pipeline(
  data_dir      = "data/",           # contains dog CSVs + static_*.CSV
  metadata_path = "data/metadata.xlsx"
)
```

## Filters applied

| Stage | Filter | Threshold | Derivation |
|---|---|---|---|
| 01 | HDOP | 4.9 | Universal (Columbus P-10 Pro) |
| 02 | Displacement speed | 5.556 m/s | Dürr & Ward (2014) |
| 03 | Turning angle | 150° | Device-level artefact (Columbus P-10 Pro) |
| 03 | Distance gate | *site-specific* | p95 positional error, static tests |
| 04 | Ellipsoidal height | *site-specific* | p99.9 height + 30 m, static tests |

## Flag interpretation

```{r}
# Each flag column is independent — combine as needed at analysis time
clean <- dog_data_flagged |>
  dplyr::filter(!flag_hdop, !flag_speed, !flag_angle, !flag_height)

# Or inspect cumulative flagging
flag_summary(dog_data_flagged)
```

## Sites without static tests

When static tests are not yet available for a site, provide manual
overrides for the site-specific thresholds:

```{r}
dog_data_flagged <- run_pipeline(
  data_dir         = "data/",
  metadata_path    = "data/metadata.xlsx",
  height_overrides = list("N'Djamena" = 450)   # ~295 m a.s.l. + 155 m buffer
)
```
